---
title: "AAPI - MDS/Cluster Analysis"
author: "Jaffa Romain"
date: "2022-08-18"
output: pdf_document
---
# BFI 10 Item Scale (Question 25)
How well do the following statements describe your personality?
I see myself as someone who ...
1) ... is reserved
2) ... is generally trusting
3) ... tends to be lazy
4) ... is relaxed, handles stress well
5) ... has few artistic interests
6) ... is outgoing, sociable
7) ... tends to find faults with others
8) ... dos a thorough job
9) ... gets nervous easily 
10) ... has an active imagination

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse); library(dplyr);library(readr);library(psych);library(tidyr);
library(janitor);library(kableExtra);library(rstatix);library(ggthemr);
library(broom);library(dtplyr);library(lme4);library(lmerTest);library(cowplot);
library(psych);library(car);library(ppcor);library(ggpubr);library(ggplot2);
library(sjstats);library(hausekeep);library(purrr);library(tidyr);
library(lavaan);library(haven);library(performance); library(apaTables)

# theme for plots
#flat, flat dark, dust, light, earth, fresh, chalk, lilac, carrot, pale, copper, grape, greyscale, sky, solarized, grass, sea, camouflage.
```

# Personality Scores
```{r data setup, message=FALSE, warning=FALSE, include=FALSE}
questionnaires <- readRDS(here::here("questionnaires.rds"))
lead_longest <- readRDS(here::here("lead_longest.rds"))
lead <- readRDS(here::here("lead.rds"))
lead_long <- readRDS(here::here("lead_long.rds"))
lead_long <- lead_long %>% mutate(Ethnicity = case_when(
  Ethnicity == "East-Asian (Chinese, Korean, Japanese)" ~ "East Asian", 
  Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)"~ "South Asian",
  Ethnicity ==  "White/Caucasian/European-American" ~ "White", 
  Ethnicity == "Black/African-American/West Indian"~ "Black"))

lead <- lead %>% mutate(Ethnicity = case_when(
  Ethnicity == "East-Asian (Chinese, Korean, Japanese)" ~ "East Asian", 
  Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)"~ "South Asian",
  Ethnicity ==  "White/Caucasian/European-American" ~ "White", 
  Ethnicity == "Black/African-American/West Indian"~ "Black"))

## setting colours

BLACK = "#383669"
EA = "#783B36"
WHITE =  "#CBB0A9"
SA = "#888B7A"
colours = c(BLACK, EA, WHITE, SA)

dem <- lead %>% group_by(Gender, Ethnicity) %>% mutate(n = n())

# dem %>% ggplot(aes(x = Ethnicity, y = count, fill = Gender)) + geom_bar(stat = "identity", position = position_dodge(),  alpha = 0.75) + theme_classic2() + geom_text(aes(label = count), size = 3, vjust = -0.1, position = position_dodge(0.9)) + labs(y = "# of Students") + scale_fill_manual(values = c("#a2decc", "#295245")) + theme(legend.title = element_blank())
```

# Leadership Scores
```{r}
initiating_structure <- lead_longest %>% filter((Survey == "Q24" &(Question == "1"| Question == "2"|Question == "3"|Question == "4"|Question == "5"|Question == "6"|Question == "7"|Question == "8"|Question == "9"|Question == "10"))) %>% group_by(Name, Rater, Survey) %>% mutate(initiation_score = mean(Score)) %>% ungroup()

consideration <- lead_longest %>% filter(Survey == "Q24" & (Question == "11"| Question == "12"|Question == "13"|Question == "14"|Question == "15"|Question == "16r"|Question == "17"|Question == "18"|Question == "19r"|Question == "20r")) %>% group_by(Name, Rater, Survey) %>% mutate(consideration_score = mean(Score))

lead_longest %>% filter(Survey == "Q25" & Question == 2) %>% group_by(Survey, Question, Gender) %>% get_summary_stats(Score, type = "mean_sd")
```


# K-Means Clustering
```{r matrix set up}
library(cluster)    # clustering algorithms
library(factoextra) # clustering algorithms & visualization

lead_longest <- lead_longest %>% mutate(type = case_when(
Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)" & Gender == "Male"  ~ "SA Male",
Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)"  & Gender == "Female"  ~ "SA Female",

Ethnicity == "East-Asian (Chinese, Korean, Japanese)"  & Gender == "Male"  ~ "EA Male",
Ethnicity == "East-Asian (Chinese, Korean, Japanese)"& Gender == "Female"  ~ "EA  Female",

Ethnicity == "White/Caucasian/European-American" & Gender == "Male"  ~ "White Male",
Ethnicity == "White/Caucasian/European-American"& Gender == "Female" ~ "White Female",

Ethnicity == "Black/African-American/West Indian"  & Gender == "Male" ~ "Black Male",
Ethnicity == "Black/African-American/West Indian" & Gender == "Female" ~  "Black Female"

))

dat <- lead_longest %>% dplyr::select(c(type, Ethnicity, Gender,   Q25_1_mean,Q25_2_mean,Q25_3_mean,  Q25_4_mean,Q25_5_mean, Q25_6_mean, Q25_7_mean , Q25_8_mean,Q25_9_mean, Q25_10_mean, Name, semester)) %>% distinct(Name, semester, .keep_all = TRUE) %>% drop_na() %>% dplyr::select(-c(semester, Name))


dat <- dat %>% mutate(Ethnicity = case_when(
  Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)"  ~ "South Asian",
Ethnicity == "East-Asian (Chinese, Korean, Japanese)"  ~ "East Asian",
Ethnicity == "White/Caucasian/European-American"~ "White",
Ethnicity == "Black/African-American/West Indian" ~ "Black"))
# take out score by ethnicity
e <- dat %>% dplyr::select(-c(Gender, type)) %>% dplyr::rename(type= "Ethnicity")
# gender
g <- dat %>% dplyr::select(-c(Ethnicity, type)) %>% dplyr::rename(type= "Gender")
# gender x ethnicity 
eg <- dat %>% dplyr::select(-c(Gender,Ethnicity)) 

dat <- rbind(e,g,eg)
dat <- aggregate(dat[, 2:11], list(dat$type), mean)
groups <- dat$Group.1
dat <- cbind(rownames(dat), data.frame(dat, row.names="Group.1")) %>% dplyr::select(-c(`rownames(dat)`))

dat <- dat %>% mutate(across(where(is.numeric), ~scale(.)))

dat <- dat %>% 
  dplyr::rename( Reserved = "Q25_1_mean",  Trusting = "Q25_2_mean",  Lazy = "Q25_3_mean", Relaxed = "Q25_4_mean", `Few Artistic` = "Q25_5_mean",  Outgoing= "Q25_6_mean", 
 `Finds Faults` = "Q25_7_mean", Thorough = "Q25_8_mean", Nervous = "Q25_9_mean", `Active imagination` = "Q25_10_mean")




set.seed(123)
final <- kmeans(dat, 3, nstart = 25)
print(final)
fviz_cluster(final, labelsize = 12, 
             palette = "jco",
             main = "", data = dat) + theme_classic() + labs(x = "Dimension 1" , y ="Dimension 2")

means <- dat %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("mean")

library(ggrepel)
distance <- get_dist(dat)
d.1 <- cmdscale(distance, 2)
data.frame(d.1, stim = groups) %>%
  ggplot(aes(x = X1, y = X2, label = stim)) + geom_point() +
  geom_text_repel(size = 2)
d.2 <- cmdscale(distance, 3, eig = TRUE)
d.2$GOF # Goodness of fit test: 0.88 with 3 variables

cluster <- final$cluster
dat$cluster <- final$cluster
data.frame(d.1, names = groups, cluster = factor(cluster)) %>%
  ggplot(aes(x = X1, y = X2, label = groups, colour = cluster)) +
  geom_point() +
  geom_text_repel(size = 2) + theme_classic2() + labs(x = "Dimension 1", y = "Dimension 2") + labs_pubr()

library(MASS)
lda.dat <-  lda(cluster ~ Reserved +  Trusting + Lazy +  Relaxed +  `Few Artistic` + Outgoing +  
          `Finds Faults` +  Thorough + 
     Nervous +  `Active imagination`, data = dat)
library(ggbiplot)

ggbiplot(lda.dat, groups = factor(cluster), labels = groups, labels.size = 4.5) +
  scale_colour_manual(values = c("#3690ad", "#d1d071", "#a0a1a7"))  + theme_classic2() + labs(fill = "Cluster", x = "", y = "" ) 
  
fviz_dist(distance, gradient = list(low = "white", mid = "#dbebd7", high = "#15402c"))


fviz_cluster(final, labelsize = 13, 
             palette = "jco",
             main = "", data = dat) +theme(legend.position="top")+ theme_classic() + labs(x = "Dimension 1" , y ="Dimension 2")
ggsave("clusters-aom.png",width = 11,height = 10,dpi=600)
```


# Plot of z-scores
```{r}
scaled_means <-  means %>% dplyr::select(-c(Cluster)) %>% scale()
scaled_means <- as.data.frame(scaled_means)

scaled_means$cluster <- means$Cluster

scaled_means <- scaled_means %>% pivot_longer(c(Reserved ,Trusting, Lazy ,Relaxed,  `Few Artistic`,  Outgoing,  `Finds Faults`, Thorough,Nervous ,`Active imagination`), names_to = 'Personality Trait', values_to = 'Score' ) %>% mutate(cluster=case_when(cluster==1~"Socially Dominant",cluster==2~"Self Contained",cluster==3~"Communally Competent" ))
library(gghighlight)

scaled_means_filtered=scaled_means %>% filter(Score<0.7&Score>-0.7)
ggplot(scaled_means,aes(`Personality Trait`, Score, fill = as.factor(cluster))) + geom_bar(stat="identity")+ geom_bar(stat="identity",data = scaled_means_filtered,color="#e0e0e0",fill="#e0e0e0") + facet_wrap(~cluster) + scale_fill_manual(values = c("#3690ad", "#d1d071", "#a0a1a7"))  + theme_classic2() + labs(fill = "Cluster" ) + theme(axis.text.x = element_text(angle =50, vjust = 1, hjust=1))+theme(
  strip.background = element_blank(),
  strip.text.x = element_blank(),legend.position="top"
)


ggplot(scaled_means,aes(`Personality Trait`, Score, fill = as.factor(cluster))) + geom_bar(stat="identity") + facet_wrap(~cluster) + scale_fill_manual(values = c("#3690ad", "#d1d071", "#a0a1a7"))  + theme_classic2() + labs(fill = "Cluster" ) + theme(axis.text.x = element_text(angle =50, vjust = 1, hjust=1))+theme(
  strip.background = element_blank(),
  strip.text.x = element_blank(),legend.position="top"
)


```
