---
title: "AAPI-revisions-analysis"
author: "Jaffa Romain"
date: "2023-08-15"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse); library(dplyr);library(readr);library(psych);library(tidyr);library(janitor);library(kableExtra);library(rstatix);library(ggthemr)
# theme for plots
#flat, flat dark, dust, light, earth, fresh, chalk, lilac, carrot, pale, copper, grape, greyscale, sky, solarized, grass, sea, camouflage.
library(tidyverse); library(broom);library(dtplyr);library(lme4);library(lmerTest);library(cowplot);library(psych);library(car);library(ppcor);library(ggpubr);library(ggplot2) ;library(sjstats);library(hausekeep);library(purrr);library(tidyr);library(lavaan);library(haven);library(performance); library(apaTables)
```

```{r data setup, message=FALSE, warning=FALSE, include=FALSE}
leadership <- read.csv("leadershipfull.csv")
lead_longest <- readRDS(here::here("lead_longest.rds"))%>% mutate(Ethnicity = case_when(
  Ethnicity == "East-Asian (Chinese, Korean, Japanese)" ~ "East Asian", 
  Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)"~ "South Asian",
  Ethnicity ==  "White/Caucasian/European-American" ~ "White", 
  Ethnicity == "Black/African-American/West Indian"~ "Black")) %>% filter(Ethnicity== "East Asian"| 
  Ethnicity == "South Asian")
lead <- readRDS(here::here("lead.rds"))%>% mutate(Ethnicity = case_when(
  Ethnicity == "East-Asian (Chinese, Korean, Japanese)" ~ "East Asian", 
  Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)"~ "South Asian",
  Ethnicity ==  "White/Caucasian/European-American" ~ "White", 
  Ethnicity == "Black/African-American/West Indian"~ "Black")) %>% filter(Ethnicity== "East Asian"| 
  Ethnicity == "South Asian")
lead_long <- readRDS(here::here("lead_long.rds"))
lead_long <- lead_long %>% mutate(Ethnicity = case_when(
  Ethnicity == "East-Asian (Chinese, Korean, Japanese)" ~ "East Asian", 
  Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)"~ "South Asian",
  Ethnicity ==  "White/Caucasian/European-American" ~ "White", 
  Ethnicity == "Black/African-American/West Indian"~ "Black")) %>% filter(Ethnicity== "East Asian"| 
  Ethnicity == "South Asian")
lead_longest=readRDS(here::here("lead_longestNEW.rds")) %>% mutate(Ethnicity = case_when(
  Ethnicity == "East-Asian (Chinese, Korean, Japanese)" ~ "East Asian", 
  Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)"~ "South Asian",
  Ethnicity ==  "White/Caucasian/European-American" ~ "White", 
  Ethnicity == "Black/African-American/West Indian"~ "Black")) %>% filter(Ethnicity== "East Asian"| 
  Ethnicity == "South Asian")

## setting colours
EA = "#CBB0A9"
SA = "#888B7A"
colors=c(EA,SA)
```

## Descriptives
```{r descriptives, message=FALSE, echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}
lead %>% tabyl(Gender, Ethnicity,) 

lead_longest %>% tabyl(rater_gender,Gender,Ethnicity)
lead_longest %>% tabyl(Gender,Ethnicity,rater_ethnicity)


lead_longest %>% mutate(question_number = as.numeric(question_number)) %>% filter(survey =="Q25" ) %>% group_by(survey, question_number, Gender) %>% get_summary_stats(rating, type = "mean_sd") %>% kable(caption = "Personality Scores by Gender") %>% kable_styling(latex_options = "striped")

lead_longest %>% mutate(question_number = as.numeric(question_number)) %>% filter(survey == "Q25" ) %>% group_by(survey, question_number, Ethnicity) %>% get_summary_stats(rating, type = "mean_sd") %>% kable(caption = "Personality Scores by Ethnicity") %>% kable_styling(latex_options = "striped") 

lead_longest=lead_longest %>% filter(rater_ethnicity=="South-East Asian (e.g., Indian, Malay, Pakistani)"|rater_ethnicity=="East-Asian (Chinese, Korean, Japanese)")
```

## Plots 
## Ethnicity and Gender - Plots and ANOVA for Personality Dimensions
```{r, echo = FALSE, warning=FALSE, message=FALSE}
theme_set(theme_pubr() +theme(legend.position = "top") )
anova_plots<-function(data,question,trait){
  df <-data  %>% filter(Question == question) %>%
  group_by(Gender, Ethnicity) %>%
  summarise( n = n(),Score = `Average Score`,
    sd = sd(`Average Score`, na.rm = TRUE),
    se = sd/sqrt(n),
    mean = mean(`Average Score`, na.rm = TRUE))
  
   ggplot(data=subset(df, !is.na(Gender) & !is.na(Ethnicity)), aes(x=Gender, y=mean, color=Ethnicity))+geom_point()+geom_line(aes(group=1), linetype="dashed")+geom_errorbar(aes(x=Gender, ymin=mean-se, ymax=mean+se), width=0.1) +  scale_color_manual(values = colors) + facet_grid(~Ethnicity)  + xlab("Gender")+ylab(trait)+labs(color="Ethnicity") +  theme(legend.title = element_blank(),legend.text = "none",
        legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 20), strip.text.x = element_text(size = 12)) +theme_pubr()
}
TWO_WAY_ANOVA<-function(lead_longest,surv,q){
  subset=lead_longest %>% filter(question_number==q&survey==surv)
  mod=lmer(data=subset,formula =rating ~ Ethnicity*Gender+(1|team))
  res=anova(mod)
  tidy=tidy(res)
  tidy$Question=q
  tidy
}
######################################################################
anova_plots(lead_long,question="Question 1",trait="Reserved")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=1)
######################################################################
anova_plots(lead_long,question="Question 2",trait="Generally trusting")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=2)
######################################################################
anova_plots(lead_long,question="Question 3",trait="Tends to be lazy")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=3)
######################################################################
anova_plots(lead_long,question="Question 4",trait="Relaxed, handles stress well")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=4)
######################################################################
anova_plots(lead_long,question="Question 5",trait="Few artistic interests")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=5)
#####################################################################
anova_plots(lead_long,question="Question 6",trait="Outgoing, sociable")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=6)
######################################################################
anova_plots(lead_long,question="Question 7",trait="Tends to find faults in others")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=7)
######################################################################
anova_plots(lead_long,question="Question 8",trait="Does a thorough job")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=8)
######################################################################
anova_plots(lead_long,question="Question 9",trait="Gets nervous easily")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=9)
######################################################################
anova_plots(lead_long,question="Question 10",trait="Has an active imagination")
TWO_WAY_ANOVA(lead_longest,surv = "Q25",q=10)
```
# Power
```{r}
subset=lead_longest %>% filter(question_number==1&survey=="Q25")
subset=subset %>% filter(!is.na(Ethnicity)&!is.na(Gender)&!is.na(team)&!is.na(rating))
  mod=lmer(data=subset,formula =rating ~ Ethnicity*Gender+(1|team))
  library(simr)
  fixef(mod)["EthnicitySouth Asian"]<--0.2
 powerSim(mod, nsim=1000, test = fcompare(rating~Ethnicity))
powerCurve(mod, nsim=1000, test = fcompare(rating~Ethnicity),along="team")
         
sjPlot::tab_model(mod)
icc(mod)
```

## Ethnicity and International Status - Plots and ANOVA for Personality Dimensions
```{r, echo = FALSE, warning=FALSE, message=FALSE}
theme_set(theme_pubr() +theme(legend.position = "top") )
anova_plots_2<-function(data,question,trait){
  df <-data  %>% filter(Question == question) %>%
  group_by(Ethnicity,`Student Status`) %>%
  summarise( n = n(),Score = `Average Score`,
    sd = sd(`Average Score`, na.rm = TRUE),
    se = sd/sqrt(n),
    mean = mean(`Average Score`, na.rm = TRUE))
  
   ggplot(data=subset(df, !is.na(`Student Status`) & !is.na(Ethnicity)), aes(x=`Student Status`, y=mean, color=Ethnicity))+geom_point()+geom_line(aes(group=1), linetype="dashed")+geom_errorbar(aes(x=`Student Status`, ymin=mean-se, ymax=mean+se), width=0.1) +  scale_color_manual(values = colors) + facet_grid(~Ethnicity)  + xlab("Student Status")+ylab(trait)+labs(color="Ethnicity") +  theme(legend.title = element_blank(),legend.text = "none",
        legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 20), strip.text.x = element_text(size = 12)) +theme_pubr()
}
TWO_WAY_ANOVA_2<-function(lead_longest,surv,q){
  subset=lead_longest %>% filter(question_number==q&survey==surv)
  mod=lmer(data=subset,formula =rating ~ Ethnicity*`Student Status`+(1|team))
  res=anova(mod)
  tidy=tidy(res)
  tidy$Question=q
  tidy
}
q=1
surv = "Q25"
  subset=lead_longest %>% filter(question_number==q&survey==surv)
model=lmer(data=subset,formula=rating ~ Ethnicity*Gender+(1|team))


######################################################################
anova_plots_2(lead_long,question="Question 1",trait="Reserved")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=1)
######################################################################
anova_plots_2(lead_long,question="Question 2",trait="Generally trusting")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=2)
######################################################################
anova_plots_2(lead_long,question="Question 3",trait="Tends to be lazy")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=3)
######################################################################
anova_plots_2(lead_long,question="Question 4",trait="Relaxed, handles stress well")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=4)
######################################################################
anova_plots_2(lead_long,question="Question 5",trait="Few artistic interests")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=5)
#####################################################################
anova_plots_2(lead_long,question="Question 6",trait="Outgoing, sociable")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=6)
######################################################################
anova_plots_2(lead_long,question="Question 7",trait="Tends to find faults in others")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=7)
######################################################################
anova_plots_2(lead_long,question="Question 8",trait="Does a thorough job")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=8)
######################################################################
anova_plots_2(lead_long,question="Question 9",trait="Gets nervous easily")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=9)
######################################################################
anova_plots_2(lead_long,question="Question 10",trait="Has an active imagination")
TWO_WAY_ANOVA_2(lead_longest,surv = "Q25",q=10)
lead_longest %>% group_by(Ethnicity,Gender,`Student Status`) %>% count()
```



## Ethnicity and Gender of Raters 
```{r}
# Plot just rater ethnicity and gender
rater_plots<-function(q,trait){
  theme_set(theme_pubr() +theme(legend.position = "top") )
df <-lead_longest  %>% filter(survey=="Q25"&question_number==q) %>%
  group_by(rater_gender,rater_ethnicity) %>%
  summarise( n = n(),Score = rating,
    sd = sd(rating, na.rm = TRUE),
    se = sd/sqrt(n),
    mean = mean(rating, na.rm = TRUE))
  BLACK = "#383669"
EA = "#783B36"
WHITE =  "#CBB0A9"
SA = "#888B7A"
colours = c(BLACK, EA, WHITE, SA)

   ggplot(data=subset(df, !is.na(rater_gender) & !is.na(rater_ethnicity)), aes(rater_gender, y=mean, color=rater_ethnicity))+geom_point()+geom_line( linetype="dashed")+geom_errorbar(aes(x=rater_gender, ymin=mean-se, ymax=mean+se), width=0.1) +  scale_color_manual(values = colours) + facet_grid(~rater_ethnicity)  + xlab("Gender")+ylab(trait)+labs(color="Ethnicity") +  theme(legend.title = element_blank(),legend.text = "none",
        legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 20), strip.text.x = element_text(size = 12)) +theme_pubr()
   
}

   three_way_anova<-function(q){
     subset=lead_longest %>% filter(survey=="Q25"&question_number==q)
  mod=lmer(data=subset,formula =rating ~ rater_gender*rater_ethnicity*Ethnicity*Gender+(1|team))
  res=anova(mod)
  res}
   
   for (q in 1:10) {
     print(three_way_anova(q))
   }
   
```
# Missingness


```{r include=FALSE}
library(visdat)
SR= readRDS(here::here("self_leadership_ratings.rds")) 
SR_TR=inner_join(lead,SR,by="Name")
```
```{r}
vis_miss(SR)
```

# Average Self-ratings 
```{r}
library(psych)
# reverse score last 2 questions
SR_TR$Q45_6 = car::recode(SR_TR$Q45_6, '1=5; 2=4; 3=3; 4=2; 5=1')
SR_TR$Q45_7 = car::recode(SR_TR$Q45_7, '1=5; 2=4; 3=3; 4=2; 5=1')

# reliability
with(SR_TR, psych::alpha(cbind(Q44_1,Q44_2,Q44_3,Q44_4,Q45_1,Q45_2,
Q45_3,Q45_4,Q45_5,Q45_6,Q45_7), na.rm=T, check.keys = TRUE)) 

SR_TR$avg_SR= rowMeans(subset(SR_TR, select = c(Q44_1,Q44_2,Q44_3,Q44_4,Q45_1,Q45_2,
Q45_3,Q45_4,Q45_5,Q45_6,Q45_7)), na.rm = TRUE)
```
```{r}
tst=SR_TR %>% dplyr::select(contains("Q")|contains("init")|contains("cons")|contains("avg_SR"))
tst=tst %>% dplyr::select(!contains("rater")&!contains("Q3")&!contains("Q19")&!contains("Q8")&!contains("Q24")&!contains("Q4"))

colnames(tst)<-c( "Reserved","Outgoing","Generally trusting", "Tends to find faults"," Tends to be lazy",
"Does a thorough job","Relaxed, handles stress well","Gets nervous easily" ,"Few artistic interests","Active imagination", "Task Leadership","Interpersonal Leadership","Self-perceived Leadership"
)
names(tst)
apa.cor.table(tst,"co.tl.doc")
library(tidyverse)
tst=lead_longest %>% distinct(Name,rater,.keep_all = T)
tst=tst %>% mutate(rater_ethnicity=case_when(rater_ethnicity=="East-Asian (Chinese, Korean, Japanese)"~"East Asian",rater_ethnicity=="South-East Asian (e.g., Indian, Malay, Pakistani)"~"South Asian")) %>% filter(!is.na(
rater_ethnicity)&!is.na(rater_gender)&!is.na(Gender)&!is.na(
Ethnicity))

tst=tst %>% mutate(same_gen=ifelse(Gender==rater_gender,1,0),same_eth=ifelse(Ethnicity==rater_ethnicity,1,0)) 
prop.table(table(tst$same_gen,tst$same_eth))

 tst%>% group_by(rater_ethnicity,rater_gender,Ethnicity,Gender)  %>% count()
tst %>% mutate(ifelse())
```

```{r}
library(ggplot2);library(ggthemr);theme('fresh');library(viridis);library(RColorBrewer);install.packages("wesanderson")
library(wesanderson)
SR_TR %>% ggplot(aes(x=Ethnicity,y=avg_SR,fill=Gender)) +
    geom_boxplot() +
    scale_fill_manual(EA,SA) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +labs(y="Average Self-reported Leadership Score")


SR_TR %>% ggplot(aes(x=Ethnicity,y=avg_SR,fill=Gender)) +
    geom_boxplot() +facet_wrap(~`Student Status`)+
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme(
      
      plot.title = element_text(size=11)
    ) +labs(y="Average Self-reported Leadership Score")

SR_TR %>% ggplot(aes(x=`Student Status`,y=avg_SR,fill=Ethnicity)) +
    geom_boxplot() +facet_wrap(~Gender)+
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme(
      plot.title = element_text(size=11)
    ) +labs(y="Average Self-reported Leadership Score")

ggplot(data=SR_TR)+geom_smooth(aes(x=avg_SR, y=initiating_structure, color=Ethnicity, linetype=Gender), method="lm", se=FALSE) + theme_cowplot()+scale_colour_manual(values=colors)+labs(x="Self-rated Leadership",y="Task Leadership",color=" Ethnicity", linetype="Gender")+ theme(legend.position="bottom", legend.text = element_text(colour="black", face="bold"), axis.text = element_text(size = 12), axis.title = element_text(size = 12), strip.text.x = element_text(size = 12)) +  guides(
         size = guide_legend(order=2))
ggsave(paste0("figuresa/is-sel","saea.png"))

ggplot(data=SR_TR)+geom_smooth(aes(x=avg_SR, y=consideration, color=Ethnicity, linetype=Gender), method="lm", se=FALSE) + theme_cowplot()+scale_colour_manual(values=colors)+labs(x="Self-rated Leadership",y="Interpersonal Leadership",color=" Ethnicity", linetype="Gender")+ theme(legend.position="bottom", legend.text = element_text(colour="black", face="bold"), axis.text = element_text(size = 12), axis.title = element_text(size = 12), strip.text.x = element_text(size = 12)) +  guides(
         size = guide_legend(order=2))
ggsave(paste0("figuresa/cons-sel","saea.png"))

summary(aov(avg_SR ~ Ethnicity*Gender, data=SR_TR))


summary(aov(initiating_structure ~ avg_SR*Ethnicity*Gender, data=SR_TR))
summary(aov(consideration ~ avg_SR*Ethnicity*Gender, data=SR_TR))

plot(SRmod)
```

```{r}

```


# LBDQ - Reliability
```{r reliability, echo=FALSE, message=FALSE, warning=FALSE}
# Initiating Structure
with(lead, alpha(cbind(Q24_1_mean, Q24_2_mean, Q24_3_mean, Q24_4_mean, Q24_5_mean, Q24_6_mean, Q24_7_mean, Q24_8_mean, Q24_9_mean, Q24_10_mean), na.rm=T, check.keys = TRUE)) 

# consideration
with(lead, alpha(cbind(Q24_11_mean, Q24_12_mean, Q24_13_mean, Q24_14_mean, Q24_15_mean, Q24_16r_mean, Q24_17_mean, Q24_18_mean, Q24_19r_mean, Q24_20r_mean), na.rm=T))



with(lead, alpha(cbind(Q24_1_mean, Q24_2_mean, Q24_3_mean, Q24_4_mean, Q24_5_mean, Q24_6_mean, Q24_7_mean, Q24_8_mean, Q24_9_mean, Q24_10_mean, Q24_11_mean, Q24_12_mean, Q24_13_mean, Q24_14_mean, Q24_15_mean, Q24_16r_mean, Q24_17_mean, Q24_18_mean, Q24_19r_mean, Q24_20r_mean), na.rm=T))
```

# Leadership Scores Data 
```{r}

initiating_structure <- lead_longest %>% filter((survey =="Q24" &(question_number== 1| question_number ==2|question_number ==3|question_number ==4|question_number ==5|question_number ==6|question_number ==7|question_number ==8|question_number ==9|question_number ==10))) %>% group_by(Name, rater, survey) %>% mutate(initiation_score = mean(rating)) %>% ungroup() 
consideration <- lead_longest %>% filter(survey =="Q24" & (question_number ==11| question_number ==12|question_number ==13|question_number ==14|question_number ==15|question_number ==16|question_number ==17|question_number ==18|question_number ==19|question_number ==20)) %>% group_by(Name, rater, survey) %>% mutate(consideration_score = mean(rating))

```

### ANOVA
```{r}

##### ANOVA ####

cons <- lmer(consideration_score~Ethnicity*Gender + (1|team), data=consideration)
anova(cons)
ini <- lmer(initiation_score~Ethnicity*Gender +  (1|team), data = initiating_structure)
anova(ini)

initiating_structure %>% group_by( Gender) %>% get_summary_stats(initiation_score, type = "mean_sd")

consideration %>% group_by(Ethnicity) %>% get_summary_stats(consideration, type = "mean_sd", )


consideration%>% ggplot(aes(x=`Student Status`,y=consideration_score,fill=Gender)) +
    geom_boxplot() +facet_wrap(~Ethnicity)+
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      plot.title = element_text(size=11)
    ) +labs(y="Average Self-reported Leadership Score")
cons <- anova(lmer(consideration_score~Ethnicity*Gender*`Student Status` + (1|team), data=consideration))

```

# Models 
```{r}
library(sjPlot)
library(sjstats)
library(MuMIn)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(apaTables)
initiating_structure <- initiating_structure %>% mutate(Ethnicity = as.factor(Ethnicity))
SR_TR_lead=SR_TR %>% dplyr::select(c(Name,avg_SR))

initiating_structure<-left_join(initiating_structure,SR_TR_lead,by="Name")

hist(initiating_structure$initiation_score)
hist(log(initiating_structure$initiation_score))

consideration <- consideration %>% mutate(Ethnicity = as.factor(Ethnicity)) 
consideration<- left_join(consideration,SR_TR_lead,by="Name")

hist(consideration$consideration_score)
hist(log(consideration$consideration_score))

### Initiating Structure - Gender Models ###
# significant
# 3 - lazy, 8 does a thorough job (conscientiousness)

genmod<-function(formul){
  genmod= lmer(formula=formul, data = initiating_structure)
print(summary(genmod))
print(Anova(genmod, type = 3) )
print(tab_model(genmod))
round(r.squaredGLMM(genmod), 3)
}
genmod(formul=initiation_score~`Student Status`+avg_SR+Gender+Ethnicity+ (1|team))
genmod(formul=initiation_score~`Student Status`+avg_SR+Gender+ (1|team))
genmod(formul=initiation_score~`Student Status`+avg_SR+Gender*Ethnicity*Q25_3_mean + Q25_8_mean + (1|team))
genmod(formul=initiation_score~`Student Status`+avg_SR+Gender*Ethnicity + Q25_3_mean + Q25_8_mean + Q25_4_mean + Q25_9_mean +  (1|team))
genmod(formul=initiation_score~`Student Status`+avg_SR+Gender*Ethnicity + Q25_3_mean + Q25_8_mean + Q25_4_mean + Q25_9_mean + Q25_1_mean  + Q25_6_mean +  (1|team))

genmod(formul=initiation_score~`Student Status`+avg_SR+Gender*Ethnicity + Q25_3_mean + Q25_8_mean + Q25_4_mean + Q25_9_mean + Q25_1_mean  + Q25_6_mean + Q25_2_mean + Q25_7_mean + Q25_5_mean + Q25_10_mean  +  (1|team))

library(nlme)
library(lme4)

### Consideration - Ethnicity ###

ethmod1 <- lmer(consideration_score~`Student Status`+avg_SR+Ethnicity+Gender+ (1|team), data = consideration)
summary(ethmod1)
Anova(ethmod1, type = 3)
tab_model(ethmod1, show.se = TRUE) 


ethmod2 <- lmer(consideration_score~`Student Status`+avg_SR+Ethnicity*Gender+ (1|team) , data = consideration)

summary(ethmod2)
Anova(ethmod2, type = 3)
tab_model(ethmod2, show.se = TRUE) 


ethmod3 <- lmer(consideration_score~`Student Status`+avg_SR+Ethnicity*Gender+ Q25_3_mean + Q25_8_mean + (1|team), data = consideration)

summary(ethmod3)
Anova(ethmod3, type = 3)
tab_model(ethmod3, show.se = TRUE) 


ethmod4 <- lmer(consideration_score~`Student Status`+avg_SR+Ethnicity*Gender+ Q25_3_mean + Q25_8_mean + Q25_4_mean + Q25_9_mean  + (1|team), data = consideration)

summary(ethmod4)
Anova(ethmod4, type = 3)
tab_model(ethmod4, show.se = TRUE) 

# marginal R - fixed
# conditional - explained by both the fixed and random effects

ethmod5 <- lmer(consideration_score~`Student Status`+avg_SR+Ethnicity*Gender+ Q25_3_mean + Q25_8_mean + Q25_4_mean + Q25_9_mean + Q25_1_mean  + Q25_6_mean + Q25_9_mean  + (1|team), data = consideration)

summary(ethmod5)
Anova(ethmod5, type = 3)
tab_model(ethmod5, show.se = TRUE) 

ethmod6 <- lmer(consideration_score~Ethnicity + Gender+ Ethnicity*Gender +  Q25_3_mean + Q25_8_mean + Q25_4_mean + Q25_9_mean + Q25_1_mean  + Q25_6_mean + Q25_2_mean + Q25_7_mean + Q25_5_mean + Q25_10_mean  + (1|team), data = consideration)

summary(ethmod6)
Anova(ethmod6, type = 3)
tab_model(ethmod6, show.se = TRUE) 
```


## Plotting means for consideration and initiating structure

```{r}
theme_set(
  theme_classic() +
    theme(legend.position = "top")
  )
dfcon.summary <-consideration %>%
  group_by(Gender, Ethnicity) %>%
  summarise( n = n(),Score = consideration_score,
    sd = sd(consideration_score, na.rm = TRUE),
    se = sd/sqrt(n),
    mean = mean(consideration_score, na.rm = TRUE)
  )

dfcon.summary2 <-consideration %>%
  group_by(Ethnicity) %>%
  summarise( n = n(),Score = consideration_score,
    sd = sd(consideration_score, na.rm = TRUE),
    se = sd/sqrt(n),
    mean = mean(consideration_score, na.rm = TRUE)
  )

consplot <-
  ggplot(data=subset(dfcon.summary2, !is.na(Ethnicity)), aes(x=Ethnicity, y=mean))+geom_point()+geom_line(aes(group=1), linetype="dashed")+geom_errorbar(aes(x=Ethnicity, ymin=mean-se, ymax=mean+se), width=0.1) +  xlab("Ethnicity")+ylab("Interpersonal leadership")+labs(color="Ethnicity") +  theme(legend.title = element_blank(),
        legend.position = "none")  + theme_classic()

consplot
ggsave("figures/consplot-saea.png")

anova(lmer(consideration_score~Ethnicity +  (1|team), data = consideration))

### initiating structure
dfis.summary <-initiating_structure %>%
  group_by(Gender, Ethnicity) %>%
  summarise( n = n(),Score = initiation_score,
    sd = sd(initiation_score, na.rm = TRUE),
    se = sd/sqrt(n),
    mean = mean(initiation_score, na.rm = TRUE)
  )

dfis.summary2 <-initiating_structure %>%
  group_by(Gender) %>%
  summarise( n = n(),Score = initiation_score,
    sd = sd(initiation_score, na.rm = TRUE),
    se = sd/sqrt(n),
    mean = mean(initiation_score, na.rm = TRUE)
  )

isplot <-
  ggplot(data=subset(dfis.summary, !is.na(Gender) & !is.na(Ethnicity)), aes(x=Gender, y=mean))+geom_point()+geom_line(aes(group=1), linetype="dashed")+geom_errorbar(aes(x=Gender, ymin=mean-se, ymax=mean+se), width=0.1) + facet_grid(~Ethnicity)  + xlab("Gender")+ylab("Task Leadership")+labs(color="Ethnicity") +  theme(legend.title = element_blank(),
        legend.position = "none") + theme_classic() 
isplot
ggsave("figures/isplot-saea.png")

ggplot(data=subset(dfis.summary2, !is.na(Gender)), aes(x=Gender, y=mean))+geom_point()+geom_line(aes(group=1), linetype="dashed")+geom_errorbar(aes(x=Gender, ymin=mean-se, ymax=mean+se), width=0.1) +  xlab("Gender")+ylab("Task Leadership")+  theme(legend.title = element_blank(),
        legend.position = "none") + theme_classic()

consplot<-function(q,t){
  new_col_name <-consideration[[paste0("Q25_", q, "_mean")]]
consideration$new_col_name <- new_col_name
  ggplot(data=consideration)+geom_smooth(aes(x=new_col_name, y=consideration_score, color=Ethnicity, linetype=Gender), method="lm", se=FALSE)+ theme_classic()+scale_colour_manual(values=colors)+labs(x=t,y="Interpersonal leadership",color=" Ethnicity", linetype="Gender")  + theme(legend.position="bottom", legend.text = element_text(colour="black", face="bold"), axis.text = element_text(size = 14), axis.title = element_text(size = 14), strip.text.x = element_text(size = 14)) +  guides(
         size = guide_legend(order=2))
  
ggsave(paste0("figuresa/con-",t,q,"-saea.png"))
}
isplot<-function(q,t){
new_col_name <-initiating_structure[[paste0("Q25_", q, "_mean")]]
initiating_structure$new_col_name <- new_col_name # replace 'mean' with the correct column if necessary
  ggplot(data=initiating_structure)+geom_smooth(aes(x=new_col_name, y=initiation_score, color=Ethnicity, linetype=Gender), method="lm", se=FALSE) + theme_cowplot()+scale_colour_manual(values=colors)+labs(x=t,y="Task Leadership",color=" Ethnicity", linetype="Gender")+ theme(legend.position="bottom", legend.text = element_text(colour="black", face="bold"), axis.text = element_text(size = 14), axis.title = element_text(size = 14), strip.text.x = element_text(size = 14)) +  guides(
         size = guide_legend(order=2))
ggsave(paste0("figuresa/is-",t,q,"-saea.png"))}


traits=list(c("Has few artistic interests",5),
c("Has an active imagination",10),
c("Tends to be lazy",3),
c("Does a thorough job",8),
c("Reserved",1),c("Outgoing",6),
c("Tends to find faults",7),c( "Generally trusting",2),
c("Gets nervous easily",9),
c("Relaxed",4))

for (tr in traits){
  consplot(q=tr[2],t=tr[1])
  }
```

# Slope Analysis

## Gender Model - task leadership
```{r}
library(rockchalk)
anova(lmer(initiation_score~Q25_2_mean*Gender +  (1|team), data = initiating_structure))

anova(lmer(initiation_score~Q25_3_mean*Gender +  (1|team), data = initiating_structure))

anova(lmer(initiation_score~Q25_4_mean*Gender +  (1|team), data = initiating_structure))



anova(lmer(initiation_score~Q25_6_mean*Gender +  (1|team), data = initiating_structure))



anova(lmer(initiation_score~Q25_8_mean*Gender +  (1|team), data = initiating_structure))

anova(lmer(initiation_score~Gender*Q25_9_mean +  (1|team), data = initiating_structure))

anova(lmer(initiation_score~Gender*Q25_10_mean +  (1|team), data = initiating_structure))

tst <- lmer(initiation_score~Q25_2_mean*Gender +  (1|team), data = initiating_structure)
# 
# plotSlopes(tst, plotx = "Q25_2_mean", modx = "gender", modxVals = "std.dev")
```





